\NAME: A framework for \\ Efficient Intrusion Detection\\ in the Internet of Things

### 2014-11-21 paper.tex
processed Danny’s remarks on abstract

When intrusion prevention fails, intrusion detection serves as a second layer
of defense. It looks for patterns \& anomalies that can indicate malicious
behavior. But supporting an adequate set of intrusion detection algorithms
imposes significant overhead on resource-constraint devices such as those in
the Internet of Things. Fusion of the algorithms, to optimize sharing of
resources, can alleviate this, yet, proves to be time-consuming, repetitive and
error-prone. To address this problem \NAME provides a framework for the
development of efficient intrusion detection systems. It consists of a domain
specific language, to formally describe intrusion detection algorithms on a
functional level, and a code generator to produce more optimally organized
source code. A side-by-side comparison shows that generated code is smaller and
reduces message passing overhead, execution time and memory footprint in
comparison to a straightforward sequential implementation of the same
algorithms.

>>>>

When intrusion prevention fails, intrusion detection serves as a second layer
of defense. It looks for patterns \& anomalies that can indicate malicious
behavior. However, supporting an adequate set of intrusion detection algorithms
imposes significant overhead on resource-constrained devices such as those in
the Internet of Things. Fusion of the algorithms reduces resource consumption
by optimizing resource sharing, yet, proves to be time-consuming, repetitive
and error-prone. To address this problem we propose \NAME, a framework for the
development of efficient intrusion detection systems. It consists of a domain
specific language, to formally describe intrusion detection algorithms on a
functional level, and a code generator to produce more optimally organized
source code. A side-by-side comparison shows that \NAME-generated code is
smaller and reduces message passing overhead, execution time and memory
footprint in comparison to a straightforward sequential implementation of the
same algorithms.
